SDG contributions

### 2023-09-06 article/article.qmd
dont restrict figure 1 to first authors.
Reason: this might overlook contributions that predominantly go to middle authors. The new approach is equivalent to full counting

normalised_region_share_time <- papers_per_country_fos_author_pos_country %>% 
  filter(author_position == "first_author") %>%
  group_by(SDG_label, year, sub_continent) %>% 
  summarise(nn = sum(n)) %>% 
  mutate(share = nn/sum(nn))
```

@@

>>>>

normalised_region_share_time <- papers_per_country_fos_author_pos_country %>% 
  group_by(SDG_label, year, sub_continent) %>% 
  summarise(nn = sum(n)) %>% 
  mutate(share = nn/sum(nn))
```

@@

This is now equivalent to full counting, since all author positions are included.
